R Notebook

### 2022-02-11 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
2.11.22
UP and at it

## Briefly describe the dataset:

1.  identify initial network format;

2.  describe and identify the nodes including:

    -   how many nodes are in the dataset;

3.  what constitutes a tie or edge including:

    -   how many ties,

    -   whether ties are directed/undirected,

    -   whether ties are weighted/binary,

    -   and how to interpret the value of the tie
        if any.

    -   Whether or not there are edge attributes
        that might be used to:

        -   subset data, or
        -   stack multiple networks.

# Week 2: Scripts

1.  [**Identify an existing data set.**]{.ul}

@@

@@

smugDnkIdx_df <- indx_SmugglerCove_recip

@@

2.  Briefly describe the network dataset.

@@

# list the structure of smugDnkIdx_df
str(smugDnkIdx_df)

# class of an object (numeric, matrix, data frame, etc)
class(smugDnkIdx_df)

# list the variables in smugDnkIdx_df
names(smugDnkIdx_df)

# dimensions of an object
dim(smugDnkIdx_df)
```
#### list the structure of smugDnkIdx_df
$ X2: chr [1:785]
$ X3: chr [1:785]
$ X5: chr [1:785]
$ X6: num [1:785]

cols(
  ..   X1 = col_skip(),
  ..   X2 = col_character(),
  ..   X3 = col_character(),
  ..   X4 = col_skip(),
  ..   X5 = col_character(),
  ..   X6 = col_double()
  .. )

#### class of an object
class(smugDnkIdx_df)
  [1] "spec_tbl_df" 
      "tbl_df"      
      "tbl"         
      "data.frame"

#### list the variables in smugDnkIdx_df
 names(smugDnkIdx_df)
[1] "X2" 
    "X3" 
    "X5" 
    "X6"
#### dimensions of an object
 dim(smugDnkIdx_df)
[1] Rows: 785   
    Cols:   4

#
## Basic R: Import & Clean Data
```{r Import }
library(tidyr)
library(readr)

smugCovIdx <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA-Data/index-by_name-Smuggler_Cove-cocktail_recipies.csv", 
                       col_names = FALSE, 
                       col_types = cols(X1 = col_skip(), 
                                                        X4 = col_skip()))
```

@@

## Basic R: Brief Dataset Description
```{r Identify critical features of data:, echo=FALSE}

dim(smugCovIdx)

colnames(smugCovIdx)

summary(smugCovIdx)

@@

# Network: Creating network Data

# Network: Describe Network Data
## 1.  *Identify and describe content of nodes and
    links,*

##2.  *Identify format of data set (i.e., matrix or
    edgelist, directed or not, weighted or not),
    and*

  network(smugDnkIdx_df)

  summary(smugDnkIdx_df,
          print.adj = TRUE
          )
```

## Create & Describe: Directed Adjacency Matrix

*Florentine Families Directed Adjacency Matrix
Network Objects:* **iGraph** smugDnkIdx_df.ig
**Statnet** smugDnkIdx_df.stat

@@

    smugDnkIdx_df.stat<-
        network(
        smugDnkIdx_df,
        directed=F,
        matrix.type="adjacency"
        )

@@

# 3. Explore the dataset using commands from week 2 tutorial.

>>>>

@@

## Basic R: Import & Clean Data

@@

smugCovIdx <- indx_SmugglerCove_recip

@@

@@

# list the structure of smugCovIdx
str(smugCovIdx)

# class of an object (numeric, matrix, data frame, etc)
class(smugCovIdx)

# list the variables in smugCovIdx
names(smugCovIdx)

# dimensions of an object
dim(smugCovIdx)
```

@@

# Network: Creating network Data
## Basic R: Brief Dataset Description
```{r Network: Identify critical features, echo=FALSE}
#### dimensions of an object
dim()

#### class of an object
class()

# list the structure of smugCovIdx
str()

# class of an object (numeric, matrix, data frame, etc)
class()

# list the variables in smugCovIdx
names()

colnames( )

summary( )

@@

## Directed Adjacency Matrix: Create & Describe

@@

    smugCovIdx.stat<-
        network(
        smugCovIdx,
        directed=F,
        matrix.type="adjacency"
        )

@@

#   Week 2: Scripts
##    Network: Describe Network Data
##    *Identify and describe content of nodes and
    links,*

##    *Identify format of data set (i.e., matrix or
    edgelist, directed or not, weighted or not),
    and*

  network(smugCovIdx)

  summary(smugCovIdx,
          print.adj = TRUE
          )
```

#       Explore the dataset using commands from week 2 tutorial.
